Tunnels to Towers: Secure Virtual Private Networking for CCN

### 2017-03-30 paper/07-experiment.tex
not at all a productive day

\begin{figure}[!t]
\centering
  \subfigure[1 Consumer x 1 Producer]{\includegraphics[width=1.5in]{images/throughput_1_1.png}\label{1a}}
  \hfil
  \subfigure[2 Consumers x 1 Producer]{\includegraphics[width=1.5in]{images/throughput_2_1.png}\label{1b}}
  \hfil
  \subfigure[3 Consumers x 1 Producer]{\includegraphics[width=1.5in]{images/throughput_3_1.png}\label{1c}}
  \hfil
  \subfigure[4 Consumers x 1 Producer]{\includegraphics[width=1.5in]{images/throughput_4_1.png}\label{1d}}
\caption{Throughput per consumer. 1 Producer X N consumers}\label{exp1}
\end{figure}

\begin{figure}[!t]
\centering
  \subfigure[1 Consumer x 1 Producer]{\includegraphics[width=1.5in]{images/throughput_1_1.png}\label{4a}}
  \hfil
  \subfigure[2 Consumers x 2 Producers]{\includegraphics[width=1.5in]{images/throughput_2_2.png}\label{4b}}
  \hfil
  \subfigure[3 Consumers x 3 Producers]{\includegraphics[width=1.5in]{images/throughput_3_3.png}\label{4c}}
  \hfil
  \subfigure[4 Consumers x 4 Producers]{\includegraphics[width=1.5in]{images/throughput_4_4.png}\label{4d}}
\caption{Throughput per consumer. N Producers X N consumers}\label{exp4}
\end{figure}

>>>>

\begin{figure}[!t]
\centering
  \subfigure[Throughput. Content packet size: 1024 bytes]{\includegraphics[width=1.5in]{images/throughput_1024.pdf}\label{1a}}
  \hfil
  \subfigure[Throughput. Content packet size: 10240 bytes]{\includegraphics[width=1.5in]{images/throughput_10240.pdf}\label{1b}}
  \hfil
  \subfigure[RTT. Content packet size: 1024 bytes]{\includegraphics[width=1.5in]{images/rtt_1024.pdf}\label{1c}}
  \hfil
  \subfigure[RTT. Content packet size: 10240 bytes]{\includegraphics[width=1.5in]{images/rtt_10240.pdf}\label{1d}}

\caption{Throughput per consumer. 1 Producer X N consumers. Content packet size: 1024B}\label{exp1}
\end{figure}
